Regression Cube Analysis of Cohort Study Data

### 2015-03-19 draft.tex
added draft for workflow

@@

\subsection{Analysis Workflow}
\begin{figure}[htb]
 \centering
 \includegraphics[width=2.8in]{figures/placeholder}
 \caption{
 \com{Workflow for different analysis approaches.}
 \com{0. Select the Variables.}
 \com{1. Select the Formulas:}
 \com{a) Analysis without hypothesis about the data set (z ~ x+y)}
 \com{b) Analysis without hypothesis with confounder (z ~ age)}
 \com{c) Analysis with hypothesis about the data set (Var ~ x+y+z)}
 \com{d) Clarify using confounder (Var ~ x)}
 \com{3. Find interesting pane.}
 \com{4. Get Details on Demand.}
 }
  \label{fig:Workflow}
\end{figure}
\com{Different Formulas work as different steps in the analysis (Fig.~\ref{fig:Workflow})}
%%
\section{System Design and Implementation} \label{Interaction- and Visualization Techniques}
%%

>>>>

\com{Restriction of amount of data because it must not be triangulated and because the ethics committees are very restrictive}

@@

\subsection{Analysis Workflow}
\begin{figure}[htb]
 \centering
 \includegraphics[width=3.0in]{figures/workflow_sketch}
 \caption{
 Workflow of the analysis using \emph{Regression Cubes}.
 %%
 The analysis starts with a set of features given by the data set.
 %%
 Then, the user may specify a formula regarding to specify a hypothesis, or use a predefined formula to start a explorative analysis of the data set.
 %%
 The Regression Cube is then visualized, where the user has either the option to adjust the formula or to derive details on demand on a specific regression.
 %%
 Insights into the data yield either an adjustment of the current formula.
 %%
 By applying a difference view, regression cubes can be compared to each other.
 %%
 The analysis yields insights and hypothesis about feature relations.
 %%
 }
  \label{fig:Workflow}
\end{figure}

\com{Different Formulas work as different steps in the analysis (Fig.~\ref{fig:Workflow})}
 \com{Workflow for different analysis approaches.}
 \com{0. Select the Variables.}
 \com{1. Select the Formulas}
 \com{a) Analysis without hypothesis about the data set (z ~ x+y)}
 \com{b) Analysis without hypothesis with confounder (z ~ age)}
 \com{c) Analysis with hypothesis about the data set (Var ~ x+y+z)}
 \com{d) Use Difference View}
 \com{d) Clarify using confounder (Var ~ x)}
 \com{3. Find interesting pane.}
 \com{4. Get Details on Demand.}
%%
Analyze first, Show Overview, Details on Demand
%%
\section{System Design and Implementation} \label{Interaction- and Visualization Techniques}
%%
